Bootstrap Confidence Intervals for Regression Discontinuity Designs

### 2016-02-15 main_paper.tex
Draft for Abstract

\begin{abstract}
This paper proves some results.
\end{abstract}

>>>>

\begin{abstract}
This paper proposes an novel bootstrap procedure to obtain robust bias-corrected
confidence intervals in regression discontinuity designs. The approach proposed 
is based on a first-order bias correction and provides an alternative
to the plug-in analytical methods proposed by Calonico, Cattaneo and Titiunik (2014).
The algorithm is simple to implement and generates robust confidence intervals
with improved coverage relative to the analytical alternatives in simulations.
\end{abstract}
